---
output: html_document
---
# Info498F Class Survey

```{r, echo=FALSE, message=FALSE}
library(plotly, warn.conflicts = FALSE)
library(dplyr)

# Read in functions from another file:
source('scripts/summary_info.R')
source('scripts/chart2.R')
source('scripts/Chart 1.R')

# Read in data
data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")

# pass data to get basic list of information about the data
summary <- summary_info(data)
```
This is a brief summary report of the data collected by the survery current info498 students took at the beginning of the quarter. In total, `r summary$participants` number of students answered this survey. Students were asked to answer `r summary$num_questions` number of basic questions mostly related to their prior experiences with computer programming.For example, students were asked to answer `r summary$questions[1:3]`.

According to the survey, `r summary$noR` number of students out of `r summary$participants` students (`r round(summary$noR / summary$participants * 100, digits = 1)`%) answered they have never used R programming language. However, they decided to take this course and explore R programming language because it seemed like most students (`r round(summary$apply / summary$participants * 100, digits = 1)`% of students) are intended to apply Informatics major at UW.



```{r, echo=FALSE, message=FALSE, warning=FALSE}
# pass data to render chart 1
# This bar graph represents number of students using different kinds of OS 
# data is also seperated by each class standing
build_plot(data)
```
- Students were asked which operating system they typically use. This bar graph represents students' OS preference. The data is also seperated by each class standing. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# pass data to render chart 2
visited_countries(data)
```

